A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-08-20 plots/cifar/aft_comparison.tex
+plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.87e+03 & -4.87e+03 & 0.8 & 0.79 & 0.01 & 0 & 0 & 0 \\
Cox & -- & -- & 0.8 & 0.79 & 0.03 & 0.02 & 0 & 0 \\
Log Logistic & -5.07e+03 & -5.07e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -5.27e+03 & -5.27e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -5.22e+03 & -5.22e+03 & 0.85 & 0.85 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.85 & 0.85 & 0.02 & 0.02 & 0 & 0 \\
Log Logistic & -5.51e+03 & -5.51e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -5.65e+03 & -5.65e+03 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-08-20 plots/cifar100/aft_comparison.tex
+plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.19e+03 & -4.19e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.77 & 0.76 & 0.01 & 0.01 & 0 & 0 \\
Log Logistic & -4.49e+03 & -4.49e+03 & 0.77 & 0.75 & 0.02 & 0.01 & 0 & 0 \\
Log Normal & -4.65e+03 & -4.65e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.4e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.81 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
Log Logistic & -4.73e+03 & -4.73e+03 & 0.82 & 0.81 & 0.01 & 0.02 & 0 & 0 \\
Log Normal & -4.89e+03 & -4.89e+03 & 0.82 & 0.81 & 0 & 0.02 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-08-20 plots/mnist/aft_comparison.tex
+plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -5.83e+03 & -5.83e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Logistic & -6.1e+03 & -6.1e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
Log Normal & -6.25e+03 & -6.25e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
